Dynamic Statistical Comparisons, and other adventures in getting organized

### 2015-05-24 talks/ilike2015.rmd
add ilike talk on dsc

---
title: "False Discovery Rates, A New Deal"
author: Matthew Stephens
date: March 9, 2015
output: ioslides_presentation
---

@@

## Before we get started: Let's get Organized!

- Over ~10 years of working with graduate students + postdocs,
I've noticed something.
- Organized researchers get more done (and better!).
- Many of them are more organized than I am!
- Thought: I should get organized; I should help others get organized.

@@

@@

## Commercial Break:

A quick ad for a recently-started project I call "Dynamic Statistical Comparisons":

- Overall Goal: Improve how the statistics and genomics (and other) communities make comparisons among methods.

@@

@@

## More on git, github, knitr, reproducibility, DSCs

- Google "The git book", to get started on git.
- Google "Karl Broman github tutorial" for statistics-oriented intro to github.
- Google "donohoe buckheit" for "Wavelab and reproducible research"
- [http://stephens999.github.io/blog/](http://stephens999.github.io/blog/) for more on DSC

## The Canonical Genomics Experiment

- Measure lots of things, with error

- Get estimates of effects $\beta_j$ ($\hat\beta_j$) and their standard errors $s_j$

- Turn these into Z-scores, $z_j = \hat\beta_j/s_j$

- Turn these into $p$ values, $p_j$

- Apply `qvalue` 
to identify findings ``significant" at a given FDR.

- ...?

## FDR, local fdr, and q values

We take a Bayesian perspective and use the following definitions
(see Storey, 2003, for connections with Frequentist definitions):

- The FDR at a threshold $P$ is 
$$\text{FDR}(P)=\Pr(\beta_j = 0 |  p_j<P).$$

- The q value for observation $j$ is $q_j=\text{FDR}(p_j)$.

- The local false discovery rate, fdr, at threshold $P$ is 
$$\text{fdr}(P) = \Pr(\beta_j =0 | p_j=P ).$$

- The fdr is more relevant, but slightly harder to estimate than 
FDR because it involves density estimation rather than tail-area estimation.

```{r, echo=FALSE}
  library("ashr") #simple simulated example
  ncz = 100 ## number of bins in z score histograms
  set.seed(111)
  hh.betahat = rnorm(1000,0,2)
  hh.sebetahat = 1
  hh.zscore = hh.betahat/hh.sebetahat
  hh.pval = pchisq(hh.zscore^2,df=1,lower.tail=F)
  hh.ash = ash(hh.betahat,hh.sebetahat, method="fdr")
  hh.q = qvalue(hh.pval)
```

```{r, echo=FALSE}
  plot_FDReg_hist = function(hh.pval,pi0,nc=40,nullcol="blue",altcol="cyan",type=4,title="Distribution of p values",...){
    hh.hist=hist(hh.pval,freq=FALSE,xlab="p value",main=title,nclass=nc,col=altcol,...)
    if(type>1){
      abline(h=pi0,col=nullcol,lwd=2)

      hh.hist$density=rep(pi0,length(hh.hist$density))  
      #hh.hist$counts=rep(hh.q$pi0*length(hh.pval)/nc,length(hh.hist$counts)) 
      plot(hh.hist,add=TRUE,col=nullcol,freq=FALSE)
    }
    if(type>2){
    abline(v=0.1,lwd=2,col=2)
    }
    if(type>3){
      text(0.05,1.2,labels="A",col=2,cex=1.2)  
      text(0.05,0.4,labels="B",col=2,cex=1.2)  
      text(0.6,3,labels=paste0("FDR = B/(A+B) =  ",round(pi0*0.1*length(hh.pval)/sum(hh.pval<0.1),2)),cex=1.2)
    }
  }
```

## Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=1)                 
```

## Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=2)                 
```

## Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=3)                 
```

## Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=4)                 
```

## Is this an important problem?

- The original paper introducing FDR (Benjamini and Hochberg, 1995) has
been cited 21,787 times (May 2014) according to Google Scholar.

- That is three times a day for the last 19 years!

## Problem 1: The Zero Assumption (ZA)

- The standard `qvalue` 
approach assumes that all the $p$ values near 1 are null.

- Analogously, one can assume that all Z scores near 0 are null. Efron refers to this as the ``Zero Assumption".

- Seems initially natural.

```{r, echo=FALSE, include=FALSE}
require(fdrtool)
  hh.fdrtool = fdrtool(hh.pval,statistic="pvalue",plot=FALSE)
require(locfdr)
  hh.locfdr = locfdr(hh.zscore,nulltype=0,plot=0)
require(mixfdr)
  hh.mixfdr = mixFdr(hh.zscore,noiseSD=1,theonull=TRUE,plot=FALSE)
```

## Implied distribution of $p$ values under $H_1$

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=4)                 
```

## Implied distribution of Z scores under alternative

```{r, echo=FALSE,fig.height=4,fig.cap=""}
#plot a histogram of z scores, highlighting the alternative distribution
#of z scores that is implied by localfdr values lfdr.
  nullalthist = function(z,lfdr,nullcol="blue",altcol="cyan",...){
    h=hist(z, freq=FALSE,col=nullcol,nclass=ncz,...)
    avlfdr = unlist(lapply(split(lfdr,cut(z,h$breaks),drop=FALSE),mean))
    h$density = (1-avlfdr) * h$density
    plot(h,add=TRUE,col=altcol,freq=FALSE)
  }

  nullalthist(hh.zscore,hh.fdrtool$lfdr)  
```

## FDR problem 2: different measurement precision

- In some cases the measurement precisions differ among units

- Eg Expression levels of low-expressed genes have less precision than high-expressed genes

- If some effects are measured less precisely than others, those tests ``lack power"
and dilute signal, increasing FDR

## Example: Mouse Heart Data

```{r, echo=FALSE}
x = read.table(paste0("../../stat45800/data/nobrega/expression/counts.txt"), header = TRUE)
xx = rowSums(x[,2:5])
x = x[xx>0,]
xx = xx[xx>0]
```

```{r echo=FALSE}
head(x)
```

- Data on 150 mouse hearts, dissected into left and right ventricle
(courtesy Scott Schmemo, Marcelo Nobrega)

```{r, echo=FALSE,include=FALSE}

load("../scratchwork/Smemo_qbinom_zdat.RData")
## two-sided test
  ttest.pval = function(t, df) {
    pval = pt(t, df = df, lower.tail = T)
    pval = 2 * ifelse(pval < 0.5, pval, 1 - pval)
    return(pval)
}

tscore = zdat[3, ]/zdat[4, ]
pval = ttest.pval(tscore, df = 2)
qval = qvalue(pval)

highxp = xx>1000 ## select high expressed genes
pval.high = pval[highxp]
qval.high = qvalue(pval.high)

zdat.ash = ash(zdat[3,],zdat[4,],df=2,method="fdr",mixcompdist="halfuniform")
zdat.ash.high = ash(zdat[3,highxp],zdat[4,highxp],df=2,method="fdr",mixcompdist="halfuniform")
zdat.ash.ES = ash(zdat[3,],zdat[4,],df=2,method="fdr",mixcompdist="halfuniform",model="ES")

```

## Example: Mouse Heart Data

```{r, echo=FALSE,fig.height=4,fig.cap=""}
qval= qvalue(pval)
plot_FDReg_hist(pval,pi0=qval$pi0,ylim=c(0,4))
```

## Mouse Data: Counts vary considerably across genes

```{r, echo=FALSE,fig.height=4,fig.cap=""}
hist(log10(xx),main="Distribution of total counts", xlab="log10(counts)")
```

## Lower count genes, less power

```{r, echo=FALSE,fig.height=4,fig.cap=""}
qval.low=qvalue(pval[!highxp])
pval.low=pval[!highxp]
plot_FDReg_hist(pval.low,pi0=qval.low$pi0,ylim=c(0,4))
```

## Higher count genes, more power
```{r, echo=FALSE, fig.height=4,fig.cap=""}
plot_FDReg_hist(pval.high,pi0=qval.high$pi0,ylim=c(0,4))
```

## Low-count genes dilute signal at high-count genes
```{r, echo=FALSE, fig.height=4,fig.cap=""}
plot_FDReg_hist(pval,pi0=qval$pi0,ylim=c(0,4))
```

## FDR problem 2: low count genes add noise, increase q values
```{r,echo=FALSE, fig.height=4,fig.cap=""}
plot(qval.high$qval,qval$qval[highxp],xlab="q values from high-count gene analysis", ylab="q values from all gene analysis", main="q values for high count genes",xlim=c(0,.5),ylim=c(0,.5))
abline(a=0,b=1,col=2)
```

## Problems: Summary

Standard tools are unduly conservative.

- The ZA, which implies actual effects have a (probably unrealistic) bimodal distribution; causes overestimate of $\pi_0$, losing power.

- By focussing on $p$ values, low-precision measurements can dilute high-precision measurements.

## FDR via Empirical Bayes

- Following previous work (e.g. Newton, Efron, Muralidharan) we take an empirical Bayes approach to FDR.

- Eg Efron assumes that the $Z$ scores come from a mixture of null, and alternative:
$$Z_j \sim f_Z(.) = \pi_0 N(.;0,1) + (1-\pi_0) f_1(.)$$
where $f_1, \pi_0$ are to be estimated from the data.

- Various semi-parametric approaches taken to estimating $f_1$. For example,
Efron uses Poisson regression; Muralidharan uses mixture of normal distributions.

- Once $f_1$ and $\pi_0$ estimated, FDR calculations are straightforward.

## FDR: A New Deal

- Instead of modelling $Z$ scores, model the effects $\beta$,
$$\beta_j \sim \pi_0 \delta_0(.) + (1-\pi_0) g(.)$$

- Constrain $g$ to be unimodal about 0; estimate $g$ from data.

- *Incorporate precision* of each observation $\hat\beta$ into the likelihood.
Specifically, approximate likelihood for $\beta_j$ by a normal: 
$$L(\beta_j) \propto \exp(-0.5 (\beta_j - \hat\beta_j)^2/s_j^2).$$
[From $\hat\beta_j \sim N(\beta_j, s_j)$]
Or, better, use a $t$ likelihood if $s_j$ estimated using few observations.

## FDR - A New Deal

@@

## FDR - A New Deal

- Alternatively, a mixture of uniforms, with 0 as one end-point of the range,
provides still more flexibility, and in particular allows for asymmetry.

- If allow a very large number of uniforms this provides the non-parametric mle for $g$; cf Grenander 1953; Cordy + Thomas 1997.

@@

- This approach actually provides a full posterior distribution for each $\beta_j$.

- So easy to obtain point estimates and credible intervals.

- Because $g(\beta)$ is unimodal, the point estimates (and CIs) will tend to be ``shrunk" towards the overall mean (0).

@@

- So we call the approach ``Adaptive Shrinkage" (ASH).

## Recall Problem 1: distribution of alternative Z values multimodal
```{r, echo=FALSE,fig.height=4,fig.cap=""}
nullalthist(hh.zscore,hh.fdrtool$lfdr,main="qvalue")  
```

## Problem Fixed: distribution of alternative Z values unimodal
```{r, echo=FALSE,fig.height=4,fig.cap=""}
nullalthist(hh.zscore,hh.ash$lfdr,main="ash")
```

## Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=4,title="qvalue")                 
```

## Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,get_pi0(hh.ash),type=4,title="ash")                 
```

## Recall Problem 2: low count genes add noise, increase q values
```{r,echo=FALSE, fig.height=4,fig.cap=""}
plot(qval.high$qval,qval$qval[highxp],xlab="q values from high-count gene analysis", ylab="q values from all gene analysis", main="q values for high count genes",xlim=c(0,.5),ylim=c(0,.5))
abline(a=0,b=1,col=2)
```

## Problem Fixed: incorporating precision reduces influence of low-count genes
```{r,echo=FALSE, fig.height=4,fig.cap=""}
plot(zdat.ash.high$qvalue,zdat.ash$qvalue[highxp],xlab="q values from high-count gene analysis", ylab="q values from all gene analysis", main="q values for high count genes",xlim=c(0,.5),ylim=c(0,.5))
abline(a=0,b=1,col=2)
```

## A new problem: an embarrassment of riches

- If the null is mostly false, the new approach can  provide unsettling results

- The FDR can be small for all observations, even those with $p \approx 1$!

- In the illustrative example, the maximum $q$ value is `r round(max(hh.ash$qvalue),2)`

## Perhaps we didn't really understand the question?

- Problem arises only if we insist on asking question ``is $\beta_j=0$?"

- Given enough signal, we become convinced that very few of the $\beta_j=0$

- But for some $\beta_j$ we still may have little information about actual value

- Suggests a change of focus: ask for which $\beta_j$ are we confident about the sign (cf Gelman et al, 2012).

## The False Sign Rate

- Suggestion: replace FDR with local false sign rate (lfsr), the probability that if we say an effect is positive (negative), it is not.

- Example: suppose we estimate that $\Pr(\beta_j<0)=0.95, \Pr(\beta_j=0) = 0.025$ and $\Pr(\beta_j>0)=0.025$. Then we report $\beta_j$ as a ``(negative) discovery", and estimate its lfsr as 0.05.

## Even with many signals, large $p$ values have high lfsr

```{r, echo=FALSE,fig.height=4,fig.cap="",warning=FALSE,message=FALSE}
  #res=data.frame(p=hh.pval, lfsr=hh.ash$lfsr, qvalue = hh.ash$qvalue)
  library("reshape2")
  res=data.frame(p=pval, lfsr=zdat.ash$lfsr, qvalue = zdat.ash$qvalue)
  res.melt = melt(res, id.vars=c("p"),variable.name="Measure")
  cbbPalette <- c("#000000", "#D55E00", "#CC79A7")
  labels = c('qvalue','lfsr')
  breaks = c("qvalue","lfsr")

  pp= ggplot(data=res.melt,aes(p,value,color=Measure)) +geom_point(shape=1) +
      geom_abline(colour = "black") +
        xlab("p-value") +
        ylab("lfsr/qvalue")

  print(pp +scale_y_continuous(limits=c(0,1)) +
          scale_x_continuous(limits=c(0,1))  +
           scale_colour_manual(values=cbbPalette,breaks=breaks,labels=labels) +
          coord_equal(ratio=1))

```

## Advantages of False Sign Rate

- The FDR is typically not actually identifiable from data.

- This is because data cannot distinguish between $\beta_j = 0$ and $\beta_j$ "very
small". So $\pi_0$ is not identifiable, and FDR is very sensitive to $\pi_0$.

- So methods for estimating $\pi_0$ and FDR, including those presented here, are designed to be ``conservative" (i.e. overestimate the FDR).

- The False Sign Rate is much less senstive to $\pi_0$, and hence more identifiable from data!

## Simulated example: $\pi_0$ not identifiable.

```{r,echo=FALSE,include=FALSE}
load("../paper/Rcode/sim1.RData") #load simulation results
source("../paper/Rcode/plot_pi0.R")
```

```{r, echo=FALSE,fig.height=4,fig.cap=""}
plot_pi0(list(simres1a))
```

## Simulated Example: so fdr not identifiable

```{r, echo=FALSE,fig.height=4,fig.cap="",warning=FALSE,message=FALSE}
source("../paper/Rcode/plot_lfsr.R")
  plot_lfsr(list(simres1a),0.1,ptype="lfdr")
```

## Simulated Example: fsr much more identifiable

```{r, echo=FALSE,fig.height=4,fig.cap="",warning=FALSE,message=FALSE}
  plot_lfsr(list(simres1a),0.1,ptype="lfsr")
```

@@

- ASH provides a generic approach to shrinkage estimation, as well as
false discovery (sign) rates.

- But by using two numbers ($\hat\beta,s$) instead of one ($p$ values or $z$ scores) varying precision of 
measurements is better accounted for.

- Unimodal assumption for effects reduces conservatism

- False Sign Rate preferable to False Discovery Rate: more identifiable, and
better representation of information in data for ``high-signal" situations.

## Other Applications

- Widely applicable: requiring only an estimated
effect size and standard error for each object.

- E.g. Currently applying it to wavelet shrinkage applications.

## Next steps?

- Incorporate shrinkage of variances and not just means. (e.g. ``moderated $t$ test", Smyth et al)

- Allow $g(\cdot;\pi)$ to depend on covariates $X$.

- Allow for correlations in the measured $\hat\beta_j$.

@@

- to the developers of **R**, **knitr**, **Rstudio** and **Pandoc**.
Also the very cool **SQUAREM** package.

@@

- Including  Chaoxing Dai, Mengyin Lu, Ester Pantaleo, Scott Powers, Sen Tian, Wei Wang, Zhengrong Xing.

>>>>

---
title: "Dynamic Statistical Comparisons, and other adventures in getting organized"
author: Matthew Stephens
date: May 22, 2015
output: ioslides_presentation
---

@@

## Getting Organized!

- Over ~10 years of working with graduate students + postdocs,
I've noticed something.
- Organized researchers get more done (and better!).
- Many of them are more organized than I am.
- Thought: I should get organized; I should help others get organized.

@@

 ![Image](screenshot.png)

@@

## More on git, github, knitr, reproducibility

- Google "The git book", to get started on git.
- Google "Karl Broman github tutorial" for statistics-oriented intro to github.
- Google "donohoe buckheit" for "Wavelab and reproducible research"

## More ridiculously-personal tips

- "Don't try to show them how clever you are" (BD Ripley)
- Minimise email for research communications 
- Chunk time
- Relax! (Exercise, Vacation)
- Admin on Fridays
- Learn some programming principles
- Benchmark early and often

## Minimise email

![Image](slack.screenshot.png)

## Benchmarking:

By which I mean, any quantitative assessment and comparisons of performance (accuracy; speed).

## Benchmarking:

Benefits include:

- Communication
- Tweaking/honing
- Basic quality assurance (cf "testing")

## Benchmarking:

Even basic benchmarks have benefits (...Done is better than perfect)

## Dynamic Statistical Comparisons

- Overall Goal: Improve how we, in the statistics community, make comparisons among methods.

- Reduce work and redundancy; make comparisons more transparent

@@

## Inspiration: Public Benchmarking

- Protein folding (CASP)

- Image analysis (Pascal)

- The Neflix Prize

- Genetics Analysis Workshop

- RECOMB/DREAM challenge

- Sage Bionetworks

@@

- [http://stephens999.github.io/blog/](http://stephens999.github.io/blog/) for more on DSC

## DSC Requirements

- Well-defined input format for methods
- Well-defined output format
- Scoring function (output, input, meta-data)
- Ways to produce input, meta-data
- Methods to turn input -> output

## DSCR - an R package

- Define Scenarios (produce input, meta-data)
- Define Methods (turn input -> output)
- Define Scores

A simple function call then runs all methods on all scenarios, outputs scores

[Simple Vignette](http://htmlpreview.github.com/?https://github.com/stephens999/dscr/blob/master/vignettes/one_sample_location.html)

## DSC examples we're working on

- Covariance Estimation
- Large-scale linear regression
- 1-D Smoothing with Wavelets [after Antoniadis et al, 2001]

## Wavelet Smoothing Example: The "Blocks" Function

```{r, echo=FALSE}
  blocks = function(n){
     t=1:n/n
    pos=c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
    hgt = 2.88/5*c(4, (-5), 3, (-4), 5, (-4.2), 2.1, 4.3, (-3.1), 2.1, (-4.2))
    mu.blk = rep(0,n)
    for(j in 1:length(pos)){
      mu.blk = mu.blk + (1 + sign(t-pos[j]))*(hgt[j]/2)
    }
    mu=0.2+0.6*(mu.blk-min(mu.blk))/max(mu.blk-min(mu.blk))
    return(mu)
  }
len = 1024
x = seq(0,1,length=len)
mu=blocks(len)
plot(x,mu,type="l",col=2,lwd=2)
y=mu+rnorm(len,0,sd=sd(mu))
points(x,y,cex=0.5)
```

## Wavelet Transform of Noisy Data

```{r,echo=FALSE}
  y.wd = wavethresh::wd(y,filter=1,family="DaubExPhase")
  plot(y.wd,first.level=5) #Haar transform
```

## Wavelet Transform of True Mean

```{r, echo=FALSE}
mu.wd = wavethresh::wd(mu,filter=1,family="DaubExPhase")
plot(mu.wd,first.level=5) #Haar transform
```

## Wavelet Shrinkage

- WCs of true mean ($$\beta$$) are "sparse" (or at least, have spiky density about 0)

- WCs for observed data ($$\betahat$$) are noisy observations of true WCs.

- If we shrink the $$\betahat$$ toward 0, they will give a better estimate for $$\beta$$

- And inverting the wavelet transform will give better estimate for $\mu$

## Shrink + Backtransform = Smooth

```{r, echo=FALSE}
y.wd.thresh = wavethresh::threshold(y.wd, policy="BayesThresh")
y.est = wavethresh::wr(y.wd.thresh)
plot(x,mu,type="l",col=2,lwd=2)
lines(x,y.est,type="l")
```

## How to Shrink?

We've been developing generic EB approaches to shrinkage estimation:

- Assume $\beta_j \sim g()$ where $g$ has some concentration about 0 ("sparse").

- Assume we have corresponding estimates $\hat\beta_j$, with standard error $s_j$.

- 
## How to Shrink?

- *Incorporate precision* of each observation $\hat\beta$ by assuming
$$\hat\beta_j | \beta_j \sim N(\beta_j, s_j^2)$$

- Constrain $g$ to be *unimodal* about 0;

- Shrink via two-stage procedure: first estimate $g$ "non-parametrically" from data; then
compute $p(\beta_j | \hat{g}, \hat\beta_j,s_j)$.

## Details

@@

@@

- Approach provides posterior distribution for each $\beta_j$.

- For wavelet shrinkage we just use posterior mean.

- Because $g(\beta)$ is unimodal, the point estimates (and CIs) will tend to be "shrunk" towards the overall mean (0).

@@

- So we call the approach "Adaptive Shrinkage" (ash).

## Smoothing with Adaptive Shrinkage (smash)

```{r, echo=FALSE, results='hide', message=FALSE}
load("../../dscr-smash/res.RData")
library("dplyr")
library("ggplot2")
res.1.v1 = res %>% filter(grepl(".1.v1",scenario)) %>% filter(method %in% c("smash.haar","smash.homo.s8","ebayesthresh","sure.homo.s8"))
PLOTNAMES=c("angles","blip","blocks","bump","corner","doppler","spike")
res.1.v1$scenario=factor(res.1.v1$scenario,levels=paste0(c("ang","blip","blk","bump","cor","dop","sp"),".1.v1"))
levels(res.1.v1$scenario)=PLOTNAMES
ggplot(res.1.v1,aes(x=method,y=mise,fill=method)) + geom_violin() + facet_grid(.~scenario) + theme(axis.text.x=element_blank())
```

## Homoskedastic errors

```{r, echo=FALSE, results='hide', message=FALSE}
res.1.v1 = res %>% filter(grepl(".1.v1",scenario)) %>% filter(method %in% c("smash.haar","smash.homo.s8","ebayesthresh"))

PLOTNAMES=c("angles","blip","blocks","bump","corner","doppler","spike")
res.1.v1$scenario=factor(res.1.v1$scenario,levels=paste0(c("ang","blip","blk","bump","cor","dop","sp"),".1.v1"))
levels(res.1.v1$scenario)=PLOTNAMES

ggplot(res.1.v1,aes(x=method,y=mise,fill=method)) + geom_violin() + facet_grid(.~scenario) +theme(axis.text.x=element_blank())
```

## Heteroskedastic errors

```{r, echo=FALSE, results='hide', message=FALSE}
res.1.v4 = res %>% filter(grepl(".1.v4",scenario)) %>% filter(method %in% c("smash.haar","smash.homo.s8","ebayesthresh"))
res.1.v4$scenario=factor(res.1.v4$scenario,levels=paste0(c("ang","blip","blk","bump","cor","dop","sp"),".1.v4"))
levels(res.1.v4$scenario)=PLOTNAMES
ggplot(res.1.v4,aes(x=method,y=mise,fill=method)) + geom_violin() + facet_grid(.~scenario) + theme(axis.text.x=element_blank())
```

## Question

- Does anyone have applications where allowing for heteroskedastic errors might be useful?

@@

- We're looking for conspirators interested in organizing benchmarking!

@@

- Zhengrong Xing

- to the developers of **R**, **knitr**, **Rstudio** and **Pandoc**.
Also the very cool **SQUAREM** and **wavethresh** packages.

@@

- Including Chaoxing Dai, Mengyin Lu, Ester Pantaleo, Scott Powers, Sen Tian, Wei Wang, .
